### 2016-12-05 Objects/Objects.tex
Adding some more on tau iso

\section{\acl{PF}}
\label{sec:objects_pf}
All stable particles are reconstructed and identified using the \ac{PF} algorithm, which
combines the information from all of the different subdetectors of \ac{CMS}. This makes
the identification of particles, and determination of position and momentum, as precise
as possible. All of these particles are then used to build for example jets, \MET and hadronically
decaying taus.

@@

\subsection{Identification}
\label{sec:objects_tau_id}
Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT algorithm with a distance parameter $\Delta R = 0.4$. 
As table \ref{tab:hadronic_tau_decays}
shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a high
probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays convert to
\APelectron \Pelectron pairs in the tracker volume, which are bent in the magnetic field and 
therefore cause showers dispersed in the $\phi$ direction in the \ac{ECAL}. Therefore, to 
reconstruct the energy deposits \Ppizero candidates leave in the ECAL, 
the photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
The \Pe or \Pphoton with highest \pT that is not yet included in a strip is used to build a new strip.
The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT \Pe or \Pphoton  
within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
recomputed as the energy-weighted average of the electron/photon constituents in the strip.
This procedure is repeated until there are no more electrons or photons with \pT $>$ 0.5$~GeV  within the 
strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the \pT or \ET to 
be added to the strip and on the energy the strip already has, as

\begin{equation}\label{eqn:dynamicstrip}
\begin{split}
&\Delta \eta  = f(\pT^{\Pe/\Pphoton}) + f(\pT^{\text{strip}}) \notag \\
&\Delta \phi  = g(\pT^{\Pe/\Pphoton}) + g(\pT^{\text{strip}})\\
\end{split}
\end{equation}

Where $\pT^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
and $\pT^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$.

The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:

\begin{equation}\label{eqn:dynamicstripfg}
\begin{split}
&f(\pT) = 0.2\cdot \pT^{-0.66} \text{ and } \notag \\
&g(\pT) = 0.35\cdot \pT^{-0.71}.\\
\end{split}
\end{equation}

If the $\Sigma \pT$ of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
compatible with a certain decay mode if the selection listed below is satisfied. 
If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT is retained.\\

The decay modes considered for reconstructing hadronic taus are:\\
\begin{itemize}
\item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{\pT/100}$~GeV. For momenta
less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{\pT/100}$~GeV. For momenta
less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
\item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate 
within $\Delta z<0.4$~cm of the same vertex, and their total charge is required to be $\pm 1$.
\end{itemize}

\subsection{Isolation and discrimination against light leptons}
\label{sec:objects_tau_iso}

>>>>

\section{\acl{PF}}
\label{sec:objects_pf}
All stable particles are reconstructed and identified using the \ac{PF} algorithm \cite{cms-pf-2009,cms-pf-2010-1,cms-pf-2010-2}, which
combines the information from all of the different subdetectors of \ac{CMS}. This makes
the identification of particles, and determination of position and momentum, as precise
as possible. All of these particles are then used to build for example jets, \MET and hadronically
decaying taus.

@@

\subsection{Identification}
\label{sec:objects_tau_id}
Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT algorithm with a distance parameter $\Delta R = 0.4$. 
As table \ref{tab:hadronic_tau_decays}
shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a high
probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays convert to
\APelectron \Pelectron pairs in the tracker volume, which are bent in the magnetic field and 
therefore cause showers dispersed in the $\phi$ direction in the \ac{ECAL}. Therefore, to 
reconstruct the energy deposits \Ppizero candidates leave in the ECAL, 
the photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
The \Pe or \Pphoton with highest \pT that is not yet included in a strip is used to build a new strip.
The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT \Pe or \Pphoton  
within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
recomputed as the energy-weighted average of the electron/photon constituents in the strip.
This procedure is repeated until there are no more electrons or photons with \pT $> 0.5$~GeV  within the 
strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the \pT or \ET to 
be added to the strip and on the energy the strip already has, as
\begin{equation}\label{eqn:dynamicstrip}
\begin{split}
&\Delta \eta  = f(p_{\text{T}}^{\Pe/\Pphoton}) + f(p_{\text{T}}^{\text{strip}}) \\
&\Delta \phi  = g(p_{\text{T}}^{\Pe/\Pphoton}) + g(p_{\text{T}}^{\text{strip}})\\
\end{split}
\end{equation}
Where \pT$^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
and \pT$^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$.

The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:
\begin{equation}\label{eqn:dynamicstripfg}
\begin{split}
&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66} \text{ and } \\
&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}.\\
\end{split}
\end{equation}
If the $\Sigma$ \pT of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
compatible with a certain decay mode if the selection listed below is satisfied. The charged particles
and strips are required to be within the signal cone $R_{\text{signal}} = \frac{3.0}{p_{\text{T}}[GeV]}$, always
required to be $0.05 < R_{\text{sig}} < 0.1$.
If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT is retained.\\

The decay modes considered for reconstructing hadronic taus are:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV. For momenta
less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}$~GeV. For momenta
less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
\item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate 
within $\Delta z<0.4$~cm of the same vertex, and their total charge is required to be $\pm 1$.
\end{itemize}

\subsection{Isolation and discrimination against light leptons}
\label{sec:objects_tau_iso}
Requiring the reconstructed $\Pgt_{h}$ to be isolated reduces the jet $\rightarrow\Pgt_{h}$ fake rate. The isolation
can be defined using a cut--based discriminator using the isolation sum,
\begin{equation}\label{eqn:cutbased_iso}
I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm }) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm }) ),
\end{equation}
where the first term denotes the sum of the transverse momenta of all charged particles not part
of the identified hadronic tau,  with \pT $> 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the 
direction of the hadronic tau, with charged particle tracks required to be compatible with having
originated from the $\Pgt_{h}$ production vertex within $d_Z < 0.2$ cm. The second term denotes the sum
of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the direction
of the hadronic tau. The effect of pile--up on this term is accounted for by subtracting the sum of the momenta of charged
particles with \pT $ > 0.5$ GeV, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
a $\Delta \beta$ factor of 0.2.

In addition to the isolation sum, a selection on the sum of transverse momenta
of electrons and photons included in strips but which are locaetd outside of the signal cone,
\begin{equation}\label{eqn:ptouter_iso}
p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt}.
\end{equation}
An  MVA $\tau_{h}$ isolation discriminator combines isolation variables with $\tau$ lifetime information into a BDT to discriminate between $\tau_{h}$ decays and quark and gluon jets.
The variables used as input are:\\
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The charged-and neutral-particle isolation sums
\item The reconstructed $\tau_{h}$ decay mode
\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outsie of the signal cone.
\end{itemize}

Figure \ref{fig:tau_iso_efficiency} compares the \Pgt identification efficiency with the
jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
MVA isolation discriminator, as well as the cut--based isolation discriminator based
on isolation sum and $\p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
discriminator performs best.

\begin{figure}
\includegraphics[width=0.7\textwidth]{./Objects/Plots/TauIsolationPlot.png}
\caption{Something about tau isolation}
\label{fig:tau_iso_efficiency}
\end{figure}
